Tidy Data

### 2014-01-14 tidy-data.tex
2.2 Data Semantics Para 1

A table is a collection of data \textbf{values}, typically either numbers (if quantitative) or strings (if qualitative). Values are grouped into \textbf{variables}, measurements of a single quantifiable property. Multiple measurements made on the same observational unit form an \textbf{observation}. An observational unit is the smallest constituent atom of the experimental unit. For example, in a longitudinal medical study, the experimental unit might be the patient, but the observational unit is the patient at each time point. In an agricultural experiment, the experimental units might be the cages given different diets, but the observational units are the pigs whose individual weights are measured. This definition of observational unit leads to variables which are physical properties, like blood pressure and weight, not conditional properties like blood pressure at time 1, or weight of pig 2.

>>>>

A table is a collection of data \textbf{values}, typically either numbers (if quantitative) or strings (if qualitative). A \textbf{variable} is a set of measurements of a single quantifiable property for multiple observational units. An \textbf{observation} is a set of measurements of multiple quantifiable properties for a single observational unit. An observational unit is the smallest constituent atom of the experimental unit. For example, in a longitudinal medical study, the experimental unit might be the patient, but the observational unit is the patient at different points in time. In an agricultural experiment, the experimental unit might be the cages assigned different diets, but the observational units are the individual pigs in those cages. In short, while an observational unit represents a conditional property, like blood pressure at time 1 or the weight of pig 2, an experimental unit represents an unconditional property, like blood pressure and weight.
